---
title: "Homework 6"
author: "Ying Jin"
date: "2020/11/28"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(modelr)
library(purrr)
```

## Problem 1

Import the dataset

```{r}
url_file = "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"

homicide_data = read_csv(url(url_file), na = c("", "NA", "Unknown"))
  
homicide_df =
  homicide_data %>% 
  mutate(
    city_state = str_c(city,state, sep = ", "),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest" ~ 0,
      disposition == "Closed by arrest" ~ 1,
    ) ,
    victim_age = as.numeric(victim_age)
  ) %>% 
  filter(!(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")),
         victim_race %in% c("Black","White")) %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

Start with one city

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

glm(resolution ~ victim_age + victim_sex + victim_race, 
    data = baltimore_df, 
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96*std.error),
    CI_upper = exp(estimate + 1.96*std.error)
  ) %>% 
  select(term, OR, starts_with("CI_")) %>% 
  knitr::kable()
```

Try this across cities

```{r}
models_results_df =
homicide_df %>% 
  nest(-city_state) %>% 
  mutate(
    models = map(.x = data, ~glm(resolution ~ victim_age + victim_sex + victim_race, 
    data = .x, 
    family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(-data, -models) %>% 
  unnest(results) %>% 
  mutate(
     OR = exp(estimate),
    CI_lower = exp(estimate - 1.96*std.error),
    CI_upper = exp(estimate + 1.96*std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI_"))
```

Make a plot

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(
    city_state = fct_reorder(city_state, OR)
  ) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) +
  theme(axis.text.x = element_text(angle = 70, hjust = 1))
```

## Problem 2

import dataset

```{r}
bwt_data = read_csv("./data/birthweight.csv")
```

tidy dataset

```{r}
bwt_df = 
bwt_data %>% 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(babysex),
    malform = as.factor(babysex),
    mrace = as.factor(babysex)
  )
```

inspect NAs

```{r}
bwt_df %>% 
  sapply(., function(x) sum(is.na(x)))
```

There is no NAs in this dataset

Then I try to build a linear model based on the dataset, which examines the association between baby birth weight and mother's pre-pregnancy BMI, age and average number of cigarettes she smokes per day during pregnancy.

```{r}
mod = lm(bwt ~ ppbmi + momage + smoken, data = bwt_df)

bwt_df %>% 
  select(bwt ,ppbmi, momage, smoken) %>% 
  add_residuals(model = mod) %>% 
  add_predictions(model = mod) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = .4)
```

Another two models:

* One using length at birth and gestational age as predictors (main effects only)

* One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

```{r}
mod_1 = lm(bwt ~ blength + gaweeks, data = bwt_df)
broom::tidy(mod_1)

mod_2 = lm(bwt ~ bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = bwt_df)
broom::tidy(mod_2)
```

Then I conduct cross validation. Firstly, split the dataset into train and test datasets.

```{r}
cv_df = crossv_mc(bwt_df, 100)
```

Fit models and obtain RMSE

```{r}
cv_df =
cv_df %>% 
  mutate(
    linear_mod_1 = map(.x = train, ~lm(bwt ~ ppbmi + momage + smoken, data = .x)),
    linear_mod_2 = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    linear_mod_3 = map(.x = train, ~lm(bwt ~ bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = .x))
  ) %>% 
  mutate(
    rmse_mod_1 = map2_dbl(.x = linear_mod_1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_mod_2 = map2_dbl(.x = linear_mod_2, .y = test, ~rmse(model = .x, data = .y)),
    rmse_mod_3 = map2_dbl(.x = linear_mod_3, .y = test, ~rmse(model = .x, data = .y))
    ) 
  
```
  
Make plots for comparison  
  
```{r}
cv_df %>% 
  select(starts_with("rmse_")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    names_prefix = "rmse_",
    values_to = "rmse"
  ) %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin()
```

